Algebraic File Synchronization: Adequacy and Completeness

### 2017-10-25 p2/ordering.tex
Full proof for the correctness of update detection
New parent function symbol
Various improvements

\begin{mydef}[$\ordersetsign$]\mlabel{def_orderset}
For a simple set or sequence of commands $S$,
we use $\orderset{S}$ to denote the set of sequences
that are all permutations of the commands in $S$
for which the following holds:
for all subsequences $\cxynv\cc\czwmv$,
\begin{itemize}
\item if $n=\parent(m)$, then $[y]=[\vald]$
\item if $\parent(n)=m$, then $y=\empt$.
\end{itemize}
\end{mydef}

@@

% TODO breaks --> not defined on

\begin{mylem}\mlabel{equiv_simple_same_commands}
If two simple sequences $A$ and $B$ are equivalent
and do not break all filesystems ($A\equiv \wrksx{B}$),
then they must contain the same commands.
\end{mylem}
\begin{proof}
% BACK_TO_THE_FS
% TODO Rule?
We use a proof by contradiction. Let $A$ and $B$ be simple sequences
such that $A\equiv \wrksx{B}$,
and $\FS$ be a filesystem that they are defined on.

We also assume that they do not contain the same commands.
Without loss of generality, we can assume
that $A$
contains $\cxynv$, and $B$ either contains a different command
$\czwnv$ on $n$, or no command on $n$ at all.
As $A$ is simple, we know that $\cxynv$ is not an assertion command,
and therefore $[x]\neq [y]$ and $\FS(n)\neq y$ as $[\FS(n)]=[x]$.
If so, then if $B$ has no command on $n$, then $B\aFS(n)=\FS(n)$ and
$A$ and $B$ cannot be equivalent.
Otherwise we know that $[z]=[x]$ as $B$ does not break $\FS$ either,
and that $w=y$ as $B\aFS(n)$ must
be $y$ and $B$ only has one command on $n$.
However, then $\czwnv=\cxynv$, which is a contradiction.
\end{proof}

@@

As a command cannot be both a construction and a desrtruction command,
this means that the indices $I^S$ are either monotone increasing, or monotone
decreasing, but cannot change direction.
And as $S$ begins with $\cxynv$ and so $I^S_0=1$, we know they are monotone increasing,
and the commands on $n_\indx$ are construction commands.
If we denote the command on $n_\indx$ with $\caaa{x_\indx}{y_\indx}{n_\indx}$,
by definition this means that $[y_\indx]\neq[\empt]$ for all $\indx$.

>>>>

\begin{mydef}[$\ordersetsign$]\mlabel{def_orderset}
For a simple set or sequence of commands $S$,
we use $\orderset{S}$ to denote the set of sequences
that are all permutations of the commands in $S$
for which the following holds:
for all subsequences $\cxynv\cc\czwmv$,
\begin{itemize}
\item if $n=\parentf{m}$, then $[y]=[\vald]$
\item if $\parentf{n}=m$, then $y=\empt$.
\end{itemize}
\end{mydef}

@@

\begin{mylem}\mlabel{equiv_simple_same_commands}
If two simple sequences $A$ and $B$ are equivalent
and do not break all filesystems ($A\equiv \wrksx{B}$),
then they must contain the same commands.
\end{mylem}
\begin{proof}
% BACK_TO_THE_FS
% TODO Rule?
Let $A$ and $B$ be simple sequences
such that $A\equiv \wrksx{B}$,
and $\FS$ be a filesystem that they are defined on.

We use a proof by contradiction, and assume that they do not contain the same commands.
Without loss of generality, we can assume
that $A$
contains $\cxynv$, and $B$ either contains a different command
$\czwnv$ on $n$, or no command on $n$ at all.
As $A$ is simple, we know that $\cxynv$ is not an assertion command,
and therefore $[x]\neq [y]$ and $\FS(n)\neq y$ as $[\FS(n)]=[x]$.
If so, then if $B$ has no command on $n$, then $B\aFS(n)=\FS(n)$ and
$A$ and $B$ cannot be equivalent.
Otherwise we know that $[z]=[x]$ as $B$ does not break $\FS$ either,
and that $w=y$ as $B\aFS(n)$ must
be $y$ and $B$ only has one command on $n$.
However, then $\czwnv=\cxynv$, which is a contradiction.
\end{proof}

@@

As a command cannot be both a construction and a destruction command,
this means that the indices $I^S$ are either monotone increasing, or monotone
decreasing, but cannot change direction.
And as $S$ begins with $\cxynv$ and so $I^S_0=1$, we know they are monotone increasing,
and the commands on $n_\indx$ are construction commands.
If we denote the command on $n_\indx$ with $\caaa{x_\indx}{y_\indx}{n_\indx}$,
by definition this means that $[y_\indx]\neq[\empt]$ for all $\indx$.

### 2017-10-25 p2/works-inverse.tex
Various improvements

\subsection{Domains of Sets and Inverses}

@@

We will write $\Dom{\sqs{A}}$ for $\bigcap_{A\in\sqs{A}} \Dom{A}$,
and $\sqs{A}\cc\sqs{B}$ for $\{A\cc B\whr A\in\sqs{A}, B\in\sqs{B}\}$.

% This has only been defined for sequences, not sets.
Moreover, we write $\wrks{\sqs{A}}$ if $\varnothing \subset \Dom{\sqs{A}}$, that is,
if we know that there is at least one filesystem
all sequences in $\sqs{A}$ are defined on.
\end{mydef}

@@

When $\sqs{A}$ or $\sqs{B}$ contains a single sequence,
we leave out the curly brackets and write,
e.g. $A\cc\sqs{B}$ to mean $\{A\}\cc\sqs{B}$,
or $\worksm{A}{B}$ to mean $\worksmbb{A}{B}$.
In particular, we write $\worksmnil{\sqs{A}}$ to mean that
there are filesystems on which all sequences in $\sqs{A}$ are defined.
If $\sqs{A}$ contains a single sequence only, $A$, this is equivalent to $\wrks{A}$.

@@

The following claim follows immediately from the definition:

>>>>

\subsection{Domains of Sets}

@@

We will write $\Dom{\sqs{A}}$ for $\bigcap_{A\in\sqs{A}} \Dom{A}$,
and $\sqs{A}\cc\sqs{B}$ for $\{A\cc B\whr A\in\sqs{A}, B\in\sqs{B}\}$.
\end{mydef}

@@

When $\sqs{A}$ or $\sqs{B}$ contains a single sequence,
we leave out the curly brackets and write,
e.g. $A\cc\sqs{B}$ to mean $\{A\}\cc\sqs{B}$,
or $\worksm{A}{B}$ to mean $\worksmbb{A}{B}$.

Also, we write $\worksmnil{\sqs{A}}$ to mean that
there are filesystems on which all sequences in $\sqs{A}$ are defined.
If $\sqs{A}$ contains a single sequence only, $A$, this is equivalent to $\wrks{A}$.

@@

The following claims follow from the definition:
